Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-02-06 arxiv/appendix-experiment.tex
refer to pdfs as opposed to eps to save space

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{\textsc{Banditron}'s final decision boundaries}
     \label{fig:banditron-points}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}'s final decision boundaries}
    \label{fig:linearova-points}
\end{figure}
%Our Algorithm with linear kernel (
%To better understand how each algorithm works,
%Our Algorithm with rational kernel (

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{Algorithm~\ref{algorithm:kernelized} (with rational kernel)'s final decision boundaries}
    \label{fig:rationalova-points}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points.pdf}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points.pdf}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{\textsc{Banditron}'s final decision boundaries}
     \label{fig:banditron-points}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points.pdf}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points.pdf}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}'s final decision boundaries}
    \label{fig:linearova-points}
\end{figure}
%Our Algorithm with linear kernel (
%To better understand how each algorithm works,
%Our Algorithm with rational kernel (

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points.pdf}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points.pdf}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{Algorithm~\ref{algorithm:kernelized} (with rational kernel)'s final decision boundaries}
    \label{fig:rationalova-points}
\end{figure}

### 2019-02-06 arxiv/empirical-comparison.tex
.
refer to pdfs as opposed to eps to save space

\begin{figure}[h]
  \centering
\begin{subfigure}[b]{0.3\textwidth}
\captionsetup{justification=centering}
\begin{center}
\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
\caption{Strongly separable case}
\label{figure:strongly-separable-dataset}
\end{center}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\captionsetup{justification=centering}
\centering
\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
\caption{Weakly separable case}
\label{figure:weakly-separable-dataset}
\end{subfigure}
\caption{Strongly and weakly linearly separable datasets in $\R^3$ with $K=3$
classes and $T=5\times 10^6$ examples. Here we show projections of the examples
onto their first two coordinates, which lie in the ball of radius $1/\sqrt{2}$
centered at the origin. The third coordinate is $1/\sqrt{2}$ for all examples.
Class 1 is depicted red. Classes 2 and 3 are depicted green and blue,
respectively. $80\%$ of the examples belong to class 1, $10\%$ belong to class 2
and $10\%$ belong to class 3. Class 1 lies in the angle interval $[-15^\circ,
15^\circ]$, while classes 2 and 3 lie in the angle intervals $[15^\circ,
180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. The examples are
strongly and weakly linearly separable with a margin of $\gamma=0.05$,
respectively. (Examples lying within margin $\gamma$ of the linear separators
were rejected during sampling.)}
\label{figure:strongly-and-weakly-separable-datasets}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.42\textwidth]{figures/strong3}
\caption{Average cumulative number of mistakes of various algorithms versus the
number of rounds for the strongly linearly separable dataset of
\autoref{figure:strongly-separable-dataset}.}
\label{figure:number-of-mistakes-strongly-separable-dataset}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.42\textwidth]{figures/weak3}
\caption{Average cumulative number of mistakes of various algorithms versus the
number of rounds for the weakly linearly separable dataset of
\autoref{figure:weakly-separable-dataset}.}
\label{figure:number-of-mistakes-weakly-separable-dataset}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
\begin{subfigure}[b]{0.3\textwidth}
\captionsetup{justification=centering}
\begin{center}
\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points.pdf}
\caption{Strongly separable case}
\label{figure:strongly-separable-dataset}
\end{center}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\captionsetup{justification=centering}
\centering
\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points.pdf}
\caption{Weakly separable case}
\label{figure:weakly-separable-dataset}
\end{subfigure}
\caption{Strongly and weakly linearly separable datasets in $\R^3$ with $K=3$
classes and $T=5\times 10^6$ examples. Here we show projections of the examples
onto their first two coordinates, which lie in the ball of radius $1/\sqrt{2}$
centered at the origin. The third coordinate is $1/\sqrt{2}$ for all examples.
Class 1 is depicted red. Classes 2 and 3 are depicted green and blue,
respectively. $80\%$ of the examples belong to class 1, $10\%$ belong to class 2
and $10\%$ belong to class 3. Class 1 lies in the angle interval $[-15^\circ,
15^\circ]$, while classes 2 and 3 lie in the angle intervals $[15^\circ,
180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. The examples are
strongly and weakly linearly separable with a margin of $\gamma=0.05$,
respectively. (Examples lying within margin $\gamma$ of the linear separators
were rejected during sampling.)}
\label{figure:strongly-and-weakly-separable-datasets}
\end{figure}

@@

\begin{minipage}{.45\textwidth}
\begin{figure}[H]
\centering
\includegraphics[width=0.98\textwidth]{figures/strong3}
\caption{Average cumulative number of mistakes of various algorithms versus the
number of rounds for the strongly linearly separable dataset of
\autoref{figure:strongly-separable-dataset}.}
\label{figure:number-of-mistakes-strongly-separable-dataset}
\end{figure}
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\begin{figure}[H]
\centering
\includegraphics[width=0.98\textwidth]{figures/weak3}
\caption{Average cumulative number of mistakes of various algorithms versus the
number of rounds for the weakly linearly separable dataset of
\autoref{figure:weakly-separable-dataset}.}
\label{figure:number-of-mistakes-weakly-separable-dataset}
\end{figure}
\end{minipage}
